They are Very Smart: Genetic-Algorithm-Based Pathfinding in Games

### 2018-12-12 paper.tex
Paper: genome and polarvector

In Figure 7, we can see the constants that are used to scale a Zombunny's
health, movement speed, and damage, which need to be set manually as discussed
in the hyperparameters sections. The Id field is used as a unique identifier if
genomes need to be looked up, and also ensures that every genome will hash differently.

@@

The mutation function in Figure 8 essentially creates a new copy of the current genome, which is then nudged by normally distributed random numbers.

>>>>

In Figure 7, we can see the constants that are used to scale a Zombunny's
health, movement speed, and damage, which need to be set manually as discussed
in the hyperparameters sections. The \texttt{Id} field is used as a unique identifier if
genomes need to be looked up, and also ensures that every genome will hash differently.

@@

The \texttt{mutation} function in Figure 8 essentially creates a new copy of the current genome, which is then nudged by normally distributed random numbers.
